R Notebook

### 2016-08-18 finalwriteup/trial_code_eq.rmd
it's been a while

library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('party')
library('randomForest')
library('RColorBrewer')
library('pwr')
library('scales')

@@

>>>>

library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('party')
library('randomForest')
library('RColorBrewer')
library('pwr')
library('scales')
library(visdat)

@@

```{r}
miss <- read.csv('C:/Users/n9232371/OneDrive/shared files/Bligh Tanner/masters/data/all9c.csv')

miss <- rename(miss, Project_type = JD.Second,
               Client_Business = Business,
               Timespan_cat = b.timespan.cbrt,
               Invoiced_cat = b.inv.log,
               Team_size = no.users,
               Loss_making = b.rpdol,
               Client_inv = client.totinv.log, 
               pc.majpos = pc.majpos.log)

# summary(miss)
vis_dat(miss %>% select(-code.client, -code.contact, -mlsto,
                        -X, -Year, -timespan.cbrt, -inv.mlsto.log,
                        -return.pdol, -Billing.Type)) +
        scale_fill_brewer(palette ='Paired')

```
```{r}
test <- read.csv('C:/Users/n9232371/OneDrive/shared files/Bligh Tanner/masters/data/all6.csv')

head(test)

test %>% filter(mlsto == "2010.165")
